Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

\begin{figure*}[htbf]
  \centering
  \scriptsize
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}

>>>>

\begin{figure*}[htbf]
  \centering
  \scriptsize
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \begin{tabular}{rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rl}
& &  & &  & &  & &  \\[-0.15cm]
Computation     & \multicolumn{1}{>{\columncolor[RGB]{  0,  , 255}}p{0.4cm}}{}  & & 
Waiting a msg.  & \multicolumn{1}{>{\columncolor[RGB]{255,  0  ,0}}p{0.4cm}}{}  & & 
Block. send     & \multicolumn{1}{>{\columncolor[RGB]{255,  0,174}}p{0.4cm}}{}  & & 
Synchronization & \multicolumn{1}{>{\columncolor[RGB]{179,  0,  0}}p{0.4cm}}{}  & & 
Wait/Wait all   & \multicolumn{1}{>{\columncolor[RGB]{235,  0,  0}}p{0.4cm}}{}  \\
& &  & &  & &  & &  \\[-0.15cm]
Immediate recv. & \multicolumn{1}{>{\columncolor[RGB]{100,100,177}}p{0.4cm}}{}  & &
I/O             & \multicolumn{1}{>{\columncolor[RGB]{172,174, 41}}p{0.4cm}}{}  & &
Group comm.     & \multicolumn{1}{>{\columncolor[RGB]{255,144, 26}}p{0.4cm}}{}  & &
Others          & \multicolumn{1}{>{\columncolor[RGB]{192,224,  0}}p{0.4cm}}{}  & &
Idle            & \multicolumn{1}{>{\columncolor[RGB]{117,195,255}}p{0.4cm}}{}  \\
\end{tabular}
  \caption{Power-perfomance traces during midday and midnight leveraging the polling and blocking MPI policies on \tinto.}
  \label{fig:11}
\end{figure*}
